---
title: Audience Engagement in Presentations 
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```
# Audience Engagement In Presentations 
### Author: Emmanuel Araba

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQYs1l6xNEDjdI9nKIN2BXwnAXJZczjyY6HdpGOq8zuS4WZo4B7y02KIlgFjYsiFnIAf2zAZIk0SV1g/pub?gid=2099547021&single=true&output=csv")
latest_data <- logged_data %>%
  rename(
    room_capacity = `How full was the room?`,
    audience_engagement = `How did most of the audience engage with the presentation?`,
    presenter_questions = `How many times did the presenter ask the audience questions?`,
    comprehension_level = `Did you find it easy to follow along in the lecture?`,
    audience_clap = `Did the audience clap at the end of the lecture/presentation?`
  )
```

### Room Capacity Visualisation 

The following chart shows the distributions of room 'fullness' that I observed across all the presentations I went to. To collect this data, I would take note of how full the room was relative to the amount of seats in the lecture theatre. For instance, some of the workshops I attended over the week were quite full, and extra chairs had to be brought in to seat all the attendees. From the plot, we can see that we had a varied range of room 'fullness', reflective of the types of presentations I attended, along with other factors like the time of day.
```{r}
# Room capacity visualisation
room_capacity_plot <- latest_data %>%
  ggplot() + 
  geom_bar(aes(x = room_capacity), fill = "salmon") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Room Capacity Distribution",
       subtitle = "How full were the lecture theatres?",
       x = "Room Capacity",
       y = "Number of Presentations")
room_capacity_plot
```

### Room 'Fullness' vs Clapping 

Next, we can visualise how the 'fullness' of presentations affects how well received the presentation was, and ultimately if the audience liked it enough to clap. Unsprisingly, presentations with low attendance seems to be relatively uninterested in the presentation, and didnt clap on any occasion. Suprisingly, as presentation attendance grew, the audience became less likely to clap at the end of a presentation.
```{r}
# Visualising clapping vs. room capacity
capacity_vs_clapping_plot <- latest_data %>%
  count(room_capacity, audience_clap) %>%
  group_by(room_capacity) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ggplot(aes(x = room_capacity, y = percentage, fill = audience_clap)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("No" = "salmon", "Yes" = "lightblue")) +
  labs(title = "Audience Clapping by Room Capacity",
       subtitle = "Are fuller rooms more likely to clap?",
       x = "Room Capacity",
       y = "Percentage",
       fill = "Audience Clapped")
capacity_vs_clapping_plot
```

### Engagement vs Clapping 

Likewise, if I observed more engagement in lectures, by grouping the various categories of engagement into one category, called 'some engagement' and having  another category called 'no engagement'. Then, we could find out if the audiences that had some engagement with the presentation were more likely to clap for their presenter. Unsurprisingly, the audiences that were engaged with the presentation applauded the presenter at the end of the presentation at a much higher rate than those that didnt.
```{r}
# Looking at the relationship between engagement and clapping
# First create a simplified engagement variable (Did engage or didn't engage)
latest_data_with_engagement_type <- latest_data %>%
  mutate(
    engagement_type = case_when(
      audience_engagement == "Didn't engage at all" ~ "No engagement",
      TRUE ~ "Some engagement"
    )
  )

# Plot engagement type vs clapping
engagement_vs_clapping_plot <- latest_data_with_engagement_type %>%
  count(engagement_type, audience_clap) %>%
  group_by(engagement_type) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ggplot(aes(x = engagement_type, y = percentage, fill = audience_clap)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  scale_fill_manual(values = c("No" = "salmon", "Yes" = "lightblue")) +
  labs(title = "Audience Clapping by Engagement Type",
       subtitle = "Does engagement correlate with clapping?",
       x = "Engagement Type",
       y = "Percentage",
       fill = "Audience Clapped")
engagement_vs_clapping_plot
```

### Summary Statistics 

And we can also find out some relevant statistics about how many questions presenters asked in their presentations.
```{r}
# Mean and median number of presenter questions
  mean_questions = mean(latest_data$presenter_questions)
  median_questions = median(latest_data$presenter_questions)
  min_questions = min(latest_data$presenter_questions)
  max_questions = max(latest_data$presenter_questions)
  
 print(paste("The mean of amount of questions asked by presenters was:", mean_questions))
 print(paste("The median of amount of questions asked by presenters was:", median_questions))
 print(paste("The minimum of amount of questions asked by presenters was:", min_questions))
 print(paste("The maximum of amount of questions asked by presenters was:", max_questions))

```

### Types of Engagement 

The following graph tracks the method of engagement I observed in the audience in each presentation. To collect this data, I took a look around the room at a random point during the presentation, and observed how most people in the room were engaging with the presentation. The sum of these options is greater than the total number of observations I made because some students would engage in multiple ways (i.e taking notes and nodding along).
```{r}
# Audience engagement methods
audience_engagement_plot <- latest_data %>%
  select(audience_engagement) %>%
  separate_rows(audience_engagement, sep = ", ") %>%
  count(audience_engagement) %>%
  ggplot() +
  geom_bar(aes(x = reorder(audience_engagement, n), y = n), stat = "identity", 
           fill = "lightblue") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Audience Engagement Methods",
       subtitle = "How did audiences engage with presentations?",
       x = "Engagement Method",
       y = "Frequency")
audience_engagement_plot
```


```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Outfit:wght@400;700&display=swap');


/* Some color variables */

:root{
  --bg: hsl(260, 5%, 98%);
  --greyBg: hsl(220, 15%, 90%);
  
  --darkText: hsl(0, 0%, 20%);
  
  --lightText: hsl(330, 5%, 55%);
  --accentText: hsl(195, 70%, 45%);
}

*{
  background-color: var(--bg);
}


/* Keeps the body centered and reduces its width to improve readability */

body {
  margin: 0 auto;
  
  width: 75%;
  max-width: 850px;
  
  background-color: inherit;
  
  font-family: Outfit, sans-serif;
  font-size: 16px;
  color: var(--darkText);
}

#learning-reflection{
  margin-bottom: 20%;
}


/* Bold headings with modified spacing */

h1{
  margin-bottom: 5px;
  
  font-weight: 700;
  line-height: 1;
}

h2{
  margin-top: 8%;
  
  font-weight: 700;
}

h4{
  margin-top: 25px;
  font-weight: 700;
}


/* Different (default) font for paragraph text */

p{
  font-family: sans-serif;
}


/* Slightly reduces the width of the image and code blocks and adds a small border around the image */

img{
  margin: 30px auto;
  display: block;
  width: 90%;
  
  padding: 10px;
  
  background-color: var(--greyBg);
  border-radius: 15px;
  
}

pre{
  margin: 50px auto;
  width: 90%;
}


/* Font weight / colour hierarchy in the header */

#header{
  margin-top: 15%;
}

.title{
  color: var(--accentText);
}

.subtitle{
  margin-top: 0;
  margin-bottom: 20px;
  
  color: var(--lightText);
}

.author{
  font-weight: 700;
}d

.author, .date{
  margin-top: 5px;
  margin-bottom: 5px;
  
  text-align: right;
}
```

